NFC and burnout in teachers - A replication and extension study

### 2022-07-20 Manuscript/Revision_Letter.Rmd
Update Revision Letter

@@

@@

@@

@@

This is our response.
\newpage

>>>>

This is our response (resolve inconsistency in tables).

@@

We revised the respective sentence that now reads:

> "... the Cronbach's Alpha of the three demand-resource-ratios in this sample were *acceptable*."

@@

[add comment on parcelling]. We used the standard bootstrapping algorithm implemented in *lavaan*. To make our procedure more transparent, we now also provide the seed and the random number generator.

@@

\Assignment{JZ \& AS}

@@

\newpage
